---
title: "ML Assignment 1"
author: "Sumit Dutt Mishra"
date: "1/31/2021"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Q1: Data Source 
Our dataset **Accounting Professionals** has been extarcted from **KAGGLE**, is a collection of databases and datasets used by machine learning community for the analysis of ML algorithms.

#### Q2: Importing Accounting Professionals data set to R Studio 
```{r}
setwd("C:\\Users\\prerak\\Desktop\\sumit")
acc_prof <- read.csv("Accounting Professionals.csv")
head(acc_prof)
``` 

#### Q3:Descriptive Statistics of acc.prof data set 
Inspecting DataSet 
```{r message=FALSE}
summary(acc_prof)
``` 
**Arithmetic Mean:** AM of a set of observation is defined as their sum divided number of observations.
```{r}
# Average Number of Years of Service
mean(acc_prof$Years.of.Service)
```

**Median:** is the middle value of the observation. 
```{r}
# Median of Age Group
median(sort(acc_prof$Age.Group))
``` 

 **Mode:** it refers to the value which occurs to the maximum frequency. 
```{r}
sort(table(acc_prof$Gender), decreasing = TRUE)


``` 

#### Q3: Transformation 
```{r}
# Applying log transformation on years of service column
log_trans <- log10(acc_prof$Years.of.Service)
#displaying first 20 values
log_trans[1:20]

```


#### Q4: Visualisation 

**Histogram Plot**
```{r message=FALSE, warning = FALSE}
library(ggplot2)
ggplot(acc_prof, aes(x = Years.Undergraduate.Study)) +
  geom_histogram() + 
  ggtitle('Histogram ')
```

**Scatter Plot**
```{r}

ggplot(acc_prof, aes(x=Years.of.Service, y=Years.Undergraduate.Study)) + 
  geom_point() +
  ggtitle('Scatter plot')
``` 




Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
